Dosage forms in antibiotic PDEs

### 2017-02-21 dosage-form/dosage-form.Rmd
removed another code

```{r load_data, message=FALSE}
dat = 2011:2014 %>%
  lapply(function(y) read_tsv(sprintf('../../data/pde_%i.tsv', y)) %>%
           select(generic_name=GNN, dosage_form_code=GCDF, dosage_form_desc=GCDF_DESC) %>%
           mutate(year=y)) %>%
  bind_rows()
```

@@

unique_combos = dat %>%
  select(dosage_form_code, dosage_form_desc) %>%
  distinct

@@

drugs_by_code = dat %>%
  filter(year == 2011) %>%
  select(generic_name, dosage_form_code) %>%
  group_by(dosage_form_code) %>%
  count(generic_name) %>%
  group_by(dosage_form_code) %>%
  do(head(., 3))

@@

drugs_by_code %>%
  mutate(keep_code=dosage_form_code %in% codes_to_keep) %>%
  rename(`generic names of top drugs with that code`=generic_name) %>%
  kable
```

>>>>

```{r load_data, message=FALSE}
dat = 2011:2014 %>%
  lapply(function(y) read_tsv(sprintf('../../data/pde_%i.tsv', y)) %>%
           select(brand_name=BN, generic_name=GNN, dosage_form_code=GCDF, dosage_form_desc=GCDF_DESC) %>%
           mutate(year=y)) %>%
  bind_rows()
```

@@

unique_combos = dat %>%
  select(dosage_form_code, dosage_form_desc) %>%
  distinct %>%
  arrange(dosage_form_code)

@@

drugs_by_code = dat %>%
  filter(year == 2011) %>%
  select(generic_name, brand_name, dosage_form_code) %>%
  group_by(dosage_form_code) %>%
  count(generic_name) %>%
  group_by(dosage_form_code) %>%
  do(head(., 3))

@@

drugs_by_code %>%
  mutate(keep_code=dosage_form_code %in% codes_to_keep) %>%
  kable
```
